Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System

### 2022-12-27 paper/paper.tex
Rivise paper. (version for oral test committee)

\begin{abstract}
In this study, we integrate a local motion planning and robust $H_\infty$ decentralized feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R). A system architecture of performing S\&R tasks for each agent in URTS is proposed to explain how to integrate reference trajectory planning and tracking control in URTS for S\&R usage. In order to optimally allocate tasks to each agent in URTS, a task allocate problem is investigated. In order to optimally plan a path for each agent in URTS to reach these allocated task locations, a path planning problem is formulated. To deal with complex S\&R terrain, we decompose the path planning problem into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning. Through such decomposition, some roadmap-based path planning algorithms can be applied to the global path planning of agents in URTS. By the behavior decision, we can decide what behavior to follow the global path according to the terrain environment. Next, we focus on the local motion planning problem of flying behavior for UAV and walking behavior for robot, and then the tracking control problem for UAVs and robots in the hybrid team system. The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail. By converting the dynamics models of UAV and robot into an unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation. Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure. With the help of MATLAB LMI Toolbox, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design problem of each UAV and robot in URTS is effectively solved. Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
\end{abstract}

@@

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose a system architecture of performing S\&R tasks for each agent in URTS to illustrate these problems and the relationship between them. The flowchart of the system architecture is also given. We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) global path planning, (iii) behavior decision, (iv) local motion planning and (v) reference tracking control. It is because the URTS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to be determined. Then, a local motion corresponding to the behavior of the agent needs to be planned. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three steps are also briefly stated.

@@

The tracking control is to control an agent to follow a desired trajectory. There are many control strategies for MAS. According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}. Centralized control means there exists a powerful central controller in MAS to gather the state information of MAS and send the control command back to each agent to reach a global goal. Due to the powerful nature of the central controller, control commands can be determined well and quickly. But when it fails, the whole system will be completely paralyzed. In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information. Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller can be avoided.

Besides, the formation control is also a topic in MAS \cite{wang2022consensus}. Its purpose is to keep a MAS in a formation while moving. Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment. In this situation, it is more reasonable to treat each agent in URTS as an independent individual to follow a specific trajectory to form a team formation.

In order to cope with the fault in the actual system, the fault-tolerant control (FTC) has also been widely studied. According to the way of handling the fault, it can be divided into the passive FTC and the active FTC \cite{6669235}. The passive FTC treats the fault as an unknown system perturbation and designs a control law to tolerate it. In contrast, the active FTC will first estimate and identify the fault and then compensate it through the controller. Despite the extra complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps. Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme is proposed to deal with the control problem in hybrid URTS.
% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
% the control problem of robot

The contributions of this study are described as follows:
\begin{enumerate}
    \item A system architecture of performing S\&R tasks for each agent in hybrid URTS are proposed so that the local motion planning and reference tracking control issues involved in each agent of hybrid URTS and their systematic relationships can be defined and resolved.
    \item A transformation between the path planned by a roadmap-based path planning algorithm and the reference trajectory required for team formation tracking control design is proposed to enable some common roadmap-based path planning algorithms to guide the team formation tracking control of agents in hybrid URTS.
    \item A general agent dynamic model is proposed so that the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC problems of the heterogeneous agents in URTS, i.e., UAVs and biped robots, can be solved together to achieve S\&R task under external disturbance and actuator and sensor fault.
\end{enumerate}

The remainder of the paper is organized as follows. In Section II, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed and the function and relationship among its components, i.e., task allocation, global path planning, behavior decision, local motion planning and tracking control are described. In Section III, the dynamics models of agents in URTS are given to plan the motion of UAV flying and biped robot walking behavior and the control strategy of agents. In Section IV, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC is proposed for the agents in URTS with the help of a general agent dynamics model. In Section V, a simulation example is given to illustrate the operation of the system architecture of performing S\&R tasks for each agent in hybrid URTS and to verify the effectiveness of the proposed tracking control method. In Section VI, a conclusion is maded.

@@

\section{PRELIMINARIES OF URTS in S\&R usage}
The URTS will start with a given S\&R area, and end with the S\&R task completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1},i=1,2,\dots,N_T$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal location determined by the task and then make a decision to avoid obstacles and other agents nearby through a path planning algorithm.
% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots if the algorithm treat the agent as a point. Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path). Furthermore, agents in URTS are not always following the path. Sometimes they need the behavior such as stop to look around, get supplies and put supplies. To meet these needs, a behavioral decision is necessary.
% The behavior decision decides an appropriate behavior based on the circumstances.

In order to make a behavior, we must plan a corresponding motion by local motion planning. The motion is a prescribed reference path for an actual mechanical system to follow. Finally, a tracking controller is designed for each agent to follow this desired reference path.

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information and distance information into the location of agents $q_{start}$ and an occupancy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see an obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Task Allocation, Global Path Planning, Behavior Decision, Local Motion Planning and Tracking Control, will be explained in the following subsections.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of performing S\&R tasks for each agent in hybrid URTS. The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as occupancy map $\mathcal{C}$ of URTS, current configuration $q_{start}$ of agents and object information of environment. The 5 blocks on right hand side are the flowchart of an agent performing a S\&R task. From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$ of agents, the planning of the path $(\sigma_n)$ of agents, the decision of the behavior $(\beta_n)$ of agents, the planning of the reference path $r[k]$ of agents corresponding to the behavior, and the low-level reference tracking control of agents. A block with two vertical lines inside in flowchart represents a predefined process which has more detailed subprocesses. The Behavior Decision block is described detailly in Fig. \ref{fig:behavior}. The Local Motion Planning block to generate the desired reference is described detailly in Fig. \ref{fig:LMP}. The Reference Tracking Control block is described detailly in Fig. \ref{fig:tracking}.}
    \label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks $T_k, k\in\mathbb{Z}$, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, each agent has different capabilities (e.g., moving speed or load capacity) and state (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, or amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs $(\alpha_{i,j}, T_k)$ to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal configuration $q_{goal}$ it needs to go at every moment. $q_{goal}$ then pass to next block, i.e., global path planning block, as shown in Fig. \ref{fig:sys}.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        The task allocation block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

\subsection{Global Path Planning}
After a goal $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ to arrive  it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithms to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner will first construct a roadmap and then use a graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Single-query planner will complete the pathfinding by constructing and querying simultaneously,
%  i.e., the roadmap will be constructed incrementally and toward the goal, 
such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner. Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such as PRM with D* search algorithm, dynamic RRT, and extended RRT. All of the above common roadmap-based planners can be applied to the proposed URTS architecture.
\textit{
    \begin{remark}
        To avoid agents colliding with each other, the concept of multi-agent path planning is proposed \cite{yu2013multi}. However, URTS operates in a large environment so the probability of collision is small and the agents have the ability to communicate. Therefore, an alternative solution is to use single-agent path planning together with the mechanism of waiting for the other agent to pass first in the event of a collision.
    \end{remark}
}

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for biped robot). In this case, an unified planner will become overly complex and impracticable. Therefore, we divide path planning into three subprocesses, i.e., global path planning, behavior decision and local motion planning. The global path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints. The local motion planning block becomes a local planner and considers the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or occupancy map) $\mathcal{C}$. $q_{start}$ and $\mathcal{C}$ is obtained by SLAM, and $q_{goal}$ is obtained by the previous block, task allocation block, as shown in Fig. \ref{fig:sys}. $\mathcal{C}$ is a space containing all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumptions are made.

@@

From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then pass to next block, i.e., behavior decision block, as shown in Fig. \ref{fig:sys}.

\textit{
    \begin{remark}
        Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be due to a goal changing that is made by human or task allocation block. For robot, it can be a collision detected by a dynamic roadmap-based planner.
    \end{remark}
}

\subsection{Behavior Decision}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Global path planning block tells agents where to go but not how since we regard the agent as a point. Therefore, agents need to determine an appropriate behavior to follow the path $(\sigma_n)$ according to the machine vision provided by the object information. Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario. These behaviors with changing position are classified as "moving" behavior in this paper. Besides, the agents in the hybrid URTS do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are classified as "action" behavior in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors can be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
where $\mathcal{B}$ is the set of behaviors. It means that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior. By the object information in Fig. \ref{fig:sys}, an appropriate behavior can be decided. However, it will be a rather complicated project, so this article will not discuss in detail. The behavior set $\mathcal{B}$ of agents in URTS can be roughly described in Fig. \ref{fig:behavior}. $(\beta_n)$ then pass to next block, i.e., local motion planning block, as shown in Fig. \ref{fig:sys}.

>>>>

\begin{abstract}
In this study, we integrate a local motion planning and robust $H_\infty$ decentralized feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R). A system architecture of performing S\&R tasks for each agent in URTS is proposed to explain how to integrate reference trajectory planning and tracking control in URTS for S\&R usage. In order to optimally allocate tasks to each agent in URTS, a task allocate problem is investigated. In order to optimally plan a path for each agent in URTS to reach these allocated task locations, a path planning problem is formulated. To deal with complex S\&R terrain, we decompose the path planning problem into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning. Through such decomposition, some roadmap-based path planning algorithms can be applied to the global path planning of agents in URTS. By the behavior decision, we can decide what behavior to follow the global path according to the terrain environment. Next, we focus on the local motion planning problem of flying behavior for UAV and walking behavior for robot, and then the tracking control problem for UAVs and robots in the hybrid team system. The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail. By converting the dynamics models of UAV and robot into an unified agent dynamic model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation. Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure. With the help of MATLAB LMI Toolbox, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design problem of each UAV and robot in URTS is effectively solved. Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
\end{abstract}

@@

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose a system architecture of performing S\&R tasks for each agent in URTS to illustrate these problems and the relationship between them. The flowchart of the system architecture is also given in Fig. \ref{fig:sys}. We divide it into five main hierarchical processes, i.e., (i) Task Allocation, (ii) Global Path Planning, (iii) Behavior Decision, (iv) Local Motion Planning and (v) Reference Tracking Control. It is because the URTS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to be determined. Then, a local motion corresponding to the behavior of the agent needs to be planned. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three steps are also briefly stated.

@@

The reference tracking control is to control an agent to follow a desired reference trajectory. There are many reference control strategies for MAS. According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}. Centralized control means there exists a powerful central controller in MAS to gather the state information of MAS and send the control command back to each agent to reach a global goal. Due to the powerful nature of the central controller, control commands can be determined well and quickly. But when it fails, the whole system will be completely paralyzed. In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information. Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller can be avoided.

Besides, the formation control is also a topic in MAS \cite{wang2022consensus}. Its purpose is to keep a MAS in a formation while moving for some allocated tasks. Although formation control provides a simple framework for the reference control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment. In this situation, it is more reasonable to treat each agent in URTS as an independent individual to be controlled to follow a specific trajectory for its allocated task to form a team formation.

In order to cope with the fault in the actual system, the fault-tolerant control (FTC) has also been widely studied. According to the way of handling the fault, it can be divided into the passive FTC and the active FTC \cite{6669235}. The passive FTC treats the fault as an unknown system perturbation and designs a control law to tolerate it. In contrast, the active FTC will first estimate and identify the fault and then compensate it through the feedback controller. Despite the extra complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps. Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme is proposed to deal with the control problem in hybrid URTS.
% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
% the control problem of robot

The contributions of this study are described as follows:
\begin{enumerate}
    \item A system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed so that the local motion planning and reference tracking control issues involved in each agent of hybrid URTS and their systematic relationships can be defined and resolved.
    \item A transformation from the path planned by a roadmap-based path planning algorithm to the reference trajectory required for team formation tracking control design is proposed to enable some common roadmap-based path planning algorithms to guide the team formation tracking control of agents in hybrid URTS to reach the goal location without obstacle collision.
    \item A general agent dynamic model is proposed so that the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC problems of the heterogeneous agents in URTS, i.e., UAVs and biped robots, can be solved together to achieve S\&R task under external disturbance and actuator and sensor fault.
\end{enumerate}

The remainder of the paper is organized as follows. In Section II, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed and the function and relationship among its components, i.e., Task Allocation, Global Path Planning, Behavior Decision, Local Motion Planning and Reference Tracking Control are described. In Section III, the dynamics models of agents in URTS are given to plan the motion of UAV flying and biped robot walking behavior and the control strategy of agents. In Section IV, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC is proposed for the agents in URTS with the help of a general agent dynamic model. In Section V, a simulation example is given to illustrate the operation of the system architecture of performing S\&R tasks for each agent in hybrid URTS and to verify the effectiveness of the proposed tracking control method. In Section VI, a conclusion is maded.

@@

\section{PRELIMINARIES OF URTS for S\&R usage}
The URTS will start with a given S\&R area, and end with the S\&R task completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1},i=1,2,\dots,N_T$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.

@@

If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal location determined by the task and then plan a path to avoid obstacles and other agents nearby through a path planning algorithm.
% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots if the algorithm treat the agent as a point. Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path). Furthermore, agents in URTS are not always following the path. Sometimes they need the behavior such as stop to look around, get supplies and put supplies. To meet these needs, a behavioral decision is necessary.

In order for the agent to make a behavior, we must plan a corresponding motion by local motion planning. The motion is a prescribed reference path for an actual mechanical system to follow. Finally, a tracking controller is designed for each agent to follow this desired reference path.

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed as shown in Fig. \ref{fig:sys}.  The detailed functions of remaining 5 blocks, i.e., Task Allocation, Global Path Planning, Behavior Decision, Local Motion Planning and Reference Tracking Control, will be explained in the following subsections.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of performing S\&R tasks for each agent in hybrid URTS. The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information. The Simultaneous Localization And Mapping (SLAM) block converts sensor information and distance information into the current configuration $q_{start}$ of agents and an occupancy map $\mathcal{C}$ of URTS. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see an obstacle and decide to climb through it). The 5 blocks on right hand side are the flowchart of an agent performing a S\&R task. From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$ of agents, the planning of the path $(\sigma_n)$ of agents, the decision of the behavior $(\beta_n)$ of agents corresponding to the path, the planning of the reference path $r[k]$ of agents corresponding to the behavior, and the low-level reference tracking control of agents. A block with two vertical lines inside in flowchart represents a predefined process which has more detailed subprocesses. Behavior Decision block is described detailly in Fig. \ref{fig:behavior}. Local Motion Planning block to generate the desired reference is described detailly in Fig. \ref{fig:LMP}. Reference Tracking Control block is described detailly in Fig. \ref{fig:tracking}.}
    \label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks $T_k, k\in\mathbb{Z}$, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, each agent has different capabilities (e.g., moving speed or load capacity) and state (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, or amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs $(\alpha_{i,j}, T_k)$ to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal configuration $q_{goal}$ it needs to go at every moment. $q_{goal}$ then passes to next block, i.e., the global path planning block, as shown in Fig. \ref{fig:sys}.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        The task allocation block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

\subsection{Global Path Planning}
After a goal configuration $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ to arrive  it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithms to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner will first construct a roadmap and then use a graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Single-query planner will complete the pathfinding by constructing and querying simultaneously, such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner. Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such as PRM with D* search algorithm, dynamic RRT, and extended RRT.
\textit{
    \begin{remark}
        To avoid agents colliding with each other, the concept of multi-agent path planning is proposed \cite{yu2013multi}. However, URTS operates in a large environment so the probability of collision is small and the agents have the ability to communicate. Therefore, an alternative solution is to use single-agent path planning together with the mechanism of waiting for the other agent to pass first in the event of a collision.
    \end{remark}
}

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for a biped robot). In this case, an unified planner will become overly complex and impracticable. Therefore, we divide path planning into three subprocesses, i.e., global path planning, behavior decision and local motion planning. The global path planning block becomes a global planner to regard an agent as a point without kinodynamic constraints. This enables the common roadmap-based path planning algorithms mentioned above to be used for global path planning in UTRS. The local motion planning block becomes a local planner to consider the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or occupancy map) $\mathcal{C}$. $q_{start}$ and $\mathcal{C}$ is obtained by SLAM, and $q_{goal}$ is obtained by the previous block, Task Allocation block, as shown in Fig. \ref{fig:sys}. $\mathcal{C}$ is a space containing all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumptions are made.

@@

From above assumptions, a path of agent can be expressed as a sequence:
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then passes to next block, i.e., the behavior decision block, as shown in Fig. \ref{fig:sys}.

\textit{
    \begin{remark}
        Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be due to a goal changing that is made by human or Task Allocation block. For robot, it can be due to a collision detected by a dynamic roadmap-based planner.
    \end{remark}
}

\subsection{Behavior Decision}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
The global path planning block tells agents where to go but not how since we regard the agent as a point. Therefore, agents need to determine an appropriate behavior to follow the path $(\sigma_n)$ according to the machine vision provided by the object information. Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario. These behaviors with changing position are classified as "Moving" behavior in this paper. Besides, the agents in the hybrid URTS do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are classified as "Action" behavior in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors can be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
where $\mathcal{B}$ is the set of behaviors. It means that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior. By the object information in Fig. \ref{fig:sys}, an appropriate behavior can be decided. However, it will be a rather complicated project, so this article will not discuss in detail. The flowchart of Behavior Decision and the behavior set $\mathcal{B}$ of agents in URTS can be roughly described in Fig. \ref{fig:behavior}. $(\beta_n)$ then passes to next block, i.e., the local motion planning block, as shown in Fig. \ref{fig:sys}.
